Limits to Spontaneous Resets in the Double-Drift Illusion

### 2019-12-16 doc/DoubleDriftResetLimits.Rmd
moving notebooks to /doc folder

@@

```{r fig.width=7, fig.height=7}
# from R/tracking_reset_pause.R
plotPostPauseTrajectories()
```

Except for one trial in participant 9, it doesn't look like there are any resets to be seen in the trajectories.

>>>>

The MEAN would say: "the majority of trials / participants show no evidence of a reset".

I'd like to be able to say: "there is no evidence of any resets in all of the data". That is hard to do, unless I find a way to do an appropriate equivalence test (where the key problem is in the word 'appropriate').

But I would settle for: "the majority of data shows no resets, and there's no easily identifiable minority in the data with resets either".

And we can do the latter if we find a measure that would be somewhat bimodal in case of a few resets. A search reveals that one of the most accepted tests is recently Hartigan's Dip Test for unimodality (H1: not unimodal), at least a few years ago, so this might have changed, but it should still work. It is in the package 'diptest'.

@@

```{r fig.width=7, fig.height=3}
# from R/tracking_reset_pause.R
plotPostPauseTrajectories()
```

Except perhaps for one trial in participant 9, it doesn't look like there are any resets to be seen in the trajectories.
